What is disputed on the web?

### 2010-02-25 papers/wicow_claimfinder/claimfinder_final.tex
Tidy up pass

\documentclass{acm_proc_article-sp}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\newcommand{\want}[1]{}
\newcommand{\idea}[1]{}
\newcommand{\note}[1]{}
\newcommand{\x}[1]{}
\newcommand{\todo}[1]{}
\newcommand{\maybe}[1]{}
\newcommand{\resolved}[1]{}

@@

\begin{document}

\toappear

@@

We present a method for the automatic acquisition of a corpus of disputed claims from the web. We consider a factual claim to be a {\it disputed claim} if a page on the web suggests both that the claim is false and also that other people say it is true.

@@

@@

In previous work, we have build an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs a user when a web page that they are reading makes a claim that it knows to be disputed by another source. For example, if a user is reading a page that says ``Elvis is alive'' and Dispute Finder recognizes this as being an instance of a known disputed claim, then Dispute Finder will highlight the text as being disputed and direct the user to other sources that put forward alternative points of view. In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to add disputed claims to its corpus manually, and by scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com). This approach scales better than having users manually mark individual pages, but it is still difficult to make this approach scale to the huge number of claims on the web that are disputed.

@@

In our work, we attempt to bypass the difficulty of contradiction detection by looking for {\it disputes} rather than {\it contradictions}. Rather than looking for claims that contradict each other, we look for linguistic clues that writers believe that there is a contradiction between what they believe and what others believe; and that this contradiction is important. 
Looking for disputes rather than contradictions allows humans to do the hard work of identifying contradictions and deciding whether they are important. If a page says ``Falsely claimed that Obama is a Muslim'' then that tells us that the author believes that other web pages are claiming that ``Obama is a Muslim'' and that the author believes this claim is false. For our purposes, disputes are also more interesting than contradictions. We are interested in the social side of dispute. We want to know who disagrees with who, why they disagree, and what they think is important.

@@

Another closely related area is sentiment analysis/opinion mining~\cite{Hu2004,Pang2004}. Opinion mining tries to determine what an author's opinion is about certain objects or certain features of certain objects. A focal application has been the automatic summarization of product reviews, to produce an overview of the product features that are viewed favorably or negatively. Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects. To put it another way, Dispute Finder can be thought of as a second order of opinion mining in which we are looking for opinions about opinions.

@@

This is an instance of pattern matching, a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for patterns such as ``$X$ such as $Y$'' to infer hyponyms; Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events; Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type; Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer  metronyms; and TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
These types of methods differ on how the patterns are generated and on how the extraction of the relevant information is performed. Most often they construct the patterns automatically and often choose them on the basis of
statistics.

In this work we simply start with an initial set of manually crafted search patterns. We then identified additional patterns by searching for the text of known disputed claims, observing what text commonly occurred as a prefix of a known disputed claim, and manually selected those patterns that made sense to us. This technique is inspired by bootstrapping algorithms~\cite{jones99bootstrapping,Girju2003,Snow2005} that start with a small number of seed words that belong to a semantic class of interest; these seed words are used to learn the extraction patterns that then can be used to extract new members of the same semantic class. In our case, the semantic entities of interest are the disputed claims. Currently, we {\em manually} choose the patterns and claims to retain, i.e., as oppose to most relevant work, we don't {\em learn} the patterns and we don't use a measure of "reliability."

@@

Since we are using a general purpose search engine, we are limited to searching for simple text strings. This requires us to generate multiple patterns that are almost the same, other than for synonyms, for example we have both ``the lie that'' vs ``the deceit that''. We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix. For example we could not search for ``say that $S$ despite'', because there is no way to require that ``despite'' and ``say that'' be in the same sentence.

In the longer term we may work round these issues by building our own search infrastructure, but Yahoo BOSS provides an excellent platform for prototyping an idea and seeing if it works.

@@

The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts. This approach has false positives and false negatives. Some web pages include dates that are not the date the article was posted, some web pages do not include the date the article was posted, and many web pages include dates in a different format. Despite being very primitive, this method seems to work reasonably well. When we manually inspected 50 pages retrieved by our algorithm, we found that 92\% written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}). We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).

@@

@@

Searching the web for patterns yields a collection of strings. From this collection, we want to filter out any strings that are not making a falsifiable claim, and any strings that make a claim that is ambiguous.

Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we want to filter some of them out. A chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might otherwise be ambiguous what entities it is referring to (case 3).

@@

We built a statistical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim. This is a classical text classification task; here the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification). Naive Bayes classifiers\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of documents\cite{mccallum98comparison}). We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and part-of-speech tag of the first and second words.

@@

In some cases a disputed claim will be followed by information about where the claim was made, or why the claim is wrong. For example ``he claimed that the moon was made of cheese {\it on his show}'' or ``he claimed that the moon is made of cheese {\it despite contrary evidence}''. We chop off such suffixes by discarding any text that follows a word such as ``despite'', ``however'', ``but'', or ``was'', provided that word was proceeded by either two noun phrases or a noun phrase and an adjective.

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=18cm]{images/2by5_bigger3_small.pdf}
	\caption{Number of claims containing a particular noun made during January of any particular year}
	\label{multiplot_nouns}
	\end{center}
\end{figure*}

@@

A corpus of disputed claims could be useful for many purposes, including real-time dispute recognition, background dispute analysis agents, and other research tools. Real-time dispute recognition agents could be used, for instance, to alert users when a trusted source disagrees with others, or to provide the user with feedback on how contentious a topic is.

Dispute Finder~\cite{Ennals2010} is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that users encounter in their lives. The current implementation of Dispute Finder is a web browser extension that highlights text on web pages that appears to make a known disputed claim. In future research, we plan to extend Dispute Finder to be able to detect disputed information in television, and in speech that a user hears during conversations. We envision a device that provides real-time feedback to users regarding claims made in a conversation or presentation. Such a device would augment individuals' intuitive recognition of that a disputed claim is being made.

Dispute analysis agents that run in the background represent another application we see for a corpus of disputed claims. Such agents could be trained with information regarding the books, journals, and news articles a user reads. It would then be able to track these subjects and alert the user when a previously-read source is now disputed. It could also track a set of topics and tell the user when something new is disputed about a topic. A background dispute analysis agent would thus serve as an automated research assistant.

A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the social dynamics of disputes on the web. As an increasing proportion of human knowledge is brought to the web, these tools will be increasingly important in sociological and historical research.

@@

We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010. This gave us a total of 7 million text strings, of which 4.2 million were identified by our classifier as being unambiguous disputable claims. This does not mean that there are 4.2 million distinct beliefs that are disputed; many of the claims in our corpus are repeating claims made elsewhere in the corpus.

@@

Figure~\ref{multiplot_nouns} shows the frequency with which particular nouns were discussed in particular years. For example the claim ``Obama is a muslim'' contains the nouns ``Obama'' and ``Muslim''. We used the NLTK~\cite{Bird2009} part-of-speech tagger to identify the nouns found in each of our claims. We then analyzed the distribution of noun frequencies in claims made between January 1st and January 31st of every year from 2000 to 2010. Although the date we searched for was in January, the claims we found are often from other points in the year, due to the noisy nature of our date search mechanism (Figure~\ref{dateaccuracy}). We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns (Figure~\ref{multiplot_nouns}). All graphs are plotted on the same scale. The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made. It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even these nouns prove to be quite interesting.

We manually inspected our claims to determine what was going on that made particular nouns spike at particular times:

\begin{itemize}
 \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention. His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections. We believe that most of the mentions of Obama before 2004 are due to date classification errors.
 \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006}.
 \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
 \item {\bf Israel:} Spikes seem to correspond to the 2009 Gaza conflict and the 2006 Lebanon conflict.
\end{itemize}

These graphs are similar to those produced by MemeTracker~\cite{Backstrom2009}, which graphed when particular memes were discussed on the web. MemeTracker tracked highly repeated phrases, rather than nouns used in disputed claims. Kittur et al~\cite{Kittur2009} graphed the categories on Wikipedia that contained the most conflict.

\begin{figure}[tbh]
 \begin{center}
  \begin{tabular}{|lll|}
    \hline
    {\bf Noun} & {\bf Word Cluster} & {\bf Freq} \\
    \hline
   {\bf children} & tiger woods abused & 218\\
                  & instead encourage daily & 178\\
    \hline
   {\bf god} & daily encourage parents & 150 \\
   \hline
   {\bf government} & health care & 1267 \\
                    & united states & 427 \\
		    & relation environmental matters & 155 \\
   \hline
   {\bf iraq} & weapons mass destruction & 373 \\
              & united states & 247 \\
	      & saddam hussein & 192 \\
	      & al qaeda & 149 \\
   \hline
   {\bf israel} & middle east & 251 \\
		& allowed upon population & 128 \\
                & united states & 107 \\
		& off map & 106 \\
   \hline
   {\bf law}    & lawbreaker rather broken & 133 \\
		& united states & 116\\
   \hline
    {\bf obama} & working best interests & 568\\
                & health care & 481\\
	        & united states & 327 \\
		& nobel prize & 270 \\
		& legitimately president & 207 \\
		& fort hood shooter hasan nidal advised & 190 \\
		& birth certificate & 180\\
   \hline
   {\bf president} & united states & 439 \\
                   & health care & 203 \\
		   & george w & 164 \\
		   & aircraft system jolting bombing & 159 \\
		   & peace prize & 125 \\
		   & white house & 125 \\
   \hline
      {\bf war} & united states & 340 \\
   \hline

   {\bf women} & stay home & 183 \\
               & save vaccine & 85 \\
   \hline
  \end{tabular}
 \end{center}
 \caption{Largest word clusters found for nouns}
  \label{cluster-figure}

@@

@@

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. For each cluster, the count is the number of claims about that noun that contain all of the words in the cluster. Most of these will make sense to people who have been following news in the United States. For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see discussion about President Ahmadinejad's alleged statement that Israel should be wiped off the map (which the authors had not previously realized was a disputed). Some of the word clusters are not particularly interesting; for example many claims talk about the United States, even when that is not an important part of what is disputed.

>>>>

\documentclass{sig-alternate}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\newcommand{\want}[1]{}
\newcommand{\idea}[1]{}
\newcommand{\note}[1]{}
\newcommand{\x}[1]{}
\newcommand{\todo}[1]{}
\newcommand{\maybe}[1]{}
\newcommand{\resolved}[1]{}

@@

\def\shortpage{\enlargethispage{-\baselineskip}}

\begin{document}
\conferenceinfo{WICOW'10,} {April 27, 2010,  Raleigh, North Carolina, USA.} 
\CopyrightYear{2010}
\crdata{978-1-60558-940-4/10/04}
\clubpenalty=10000
\widowpenalty = 10000

@@

We present a method for automatically acquiring of a corpus of disputed claims from the web. We consider a factual claim to be {\it disputed} if a page on the web suggests both that the claim is false and also that other people say it is true.

@@

\shortpage

@@

In previous work, we built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs a user when a web page makes a claim that is in its database of known disputed claims. For example, if a user is reading a page that says ``Elvis is alive'' and Dispute Finder recognizes this as being an instance of a known disputed claim, then Dispute Finder will highlight the text as being disputed and direct the user to web pages that put forward alternative points of view. In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to add disputed claims to its corpus manually, and by scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com). This approach scales better than having users manually mark individual pages, but it is still difficult to make this approach scale to the huge number of claims on the web that are disputed.

@@

In our work, we attempt to bypass the difficulty of contradiction detection by looking for {\it disputes} rather than contradictions. Rather than looking for claims that contradict each other, we look for linguistic clues that writers believe that there is a contradiction between what they believe and what others believe; and that this contradiction is important. 
Looking for disputes rather than contradictions allows humans to do the hard work of identifying contradictions and deciding whether they are important. If a page says ``Falsely claimed that Obama is a Muslim'' then that tells us that the author believes that other web pages are claiming that ``Obama is a Muslim'' and that the author believes this claim is false. For our purposes, disputes are also more interesting than contradictions; we are interested in the social side of dispute; we want to know who disagrees with who, why they disagree, and what they think is important.

@@

Another closely related area is sentiment analysis/opinion mining~\cite{Hu2004,Pang2004}. Opinion mining tries to determine what an author's opinion is about certain objects or certain features of certain objects. A focal application has been automatically summarizing of product reviews to produce an overview of the product features that are viewed favorably or negatively. Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects. To put it another way, dispute mining can be thought of as a second order of opinion mining in which we are looking for opinions about opinions.

@@

This is an instance of pattern matching, a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for patterns such as ``$X$ such as $Y$'' to infer hyponyms; Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events; Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type; Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer  metronyms; and Text-Runner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
These types of methods differ on how the patterns are generated and on how the extraction of the relevant information is performed. Most often they construct the patterns automatically and often choose them on the basis of
statistics.

In this work we started with an initial set of manually crafted search patterns. We then identified additional patterns by searching for the text of known disputed claims, observing what text commonly occurred as a prefix of a known disputed claim, and manually choosing those patterns that made sense to us. This technique is inspired by bootstrapping algorithms~\cite{jones99bootstrapping,Girju2003,Snow2005} that start with a small number of seed items that belong to a semantic class of interest and use these seed items to learn extraction patterns that can be used to find new members of the same semantic class. In our case, the semantic entities of interest are the disputed claims. Currently, we {\em manually} choose the patterns to retain, rather than having the algorithm pick the patterns automatically.

@@

Since we are using a general purpose search engine, we are limited to searching for simple text strings. This requires us to generate multiple patterns that use different synonyms of the same word; for example we have both ``the lie that'' and ``the deceit that''. We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix. For example we could not search for ``say that $S$ despite'', because there is no way to require that ``despite'' and ``say that'' be in the same sentence.

In the longer term we may work round these issues by building our own search infrastructure, but Yahoo BOSS provides an excellent platform for prototyping the idea to see if it works.

@@

The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts. This approach has false positives and false negatives. Some web pages include dates that are not the date the article was posted, some web pages do not include the date the article was posted, and many web pages include dates in a different format. Despite being very primitive, this method seems to work reasonably well. When we manually inspected 50 pages retrieved by our algorithm, we found that 92\% were written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}). We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).

@@

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=18.1cm]{images/2by5_bigger3_small.pdf}
	\caption{Number of claims containing a particular noun made during January of any particular year}
	\label{multiplot_nouns}
	\end{center}
	\vspace{0.6cm}
\end{figure*}

@@

Searching the web for patterns yields a collection of strings. From this collection we want to filter out any strings that are not making a falsifiable claim and any strings that make a claim that is ambiguous.

Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we want to filter some of them out. A chunk of text might not be a statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might otherwise be ambiguous what entities it is referring to (case 3).

@@

We built a statistical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim. This is a classical text classification task where the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification). Naive Bayes classifiers~\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of a document~\cite{mccallum98comparison}). We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and part-of-speech tag of the first and second words.

\shortpage

@@

In some cases a disputed claim will be followed by information about where the claim was made, or why the claim is wrong. For example ``he claimed that the moon was made of cheese {\it on his show}'' or ``he claimed that the moon is made of cheese {\it despite contrary evidence}''. We chop off such suffixes by discarding any text that follows a word such as ``despite'', ``however'', ``but'', or ``was'', provided that word was proceeded by something that looks like a statement.

@@

There are many potential uses for a corpus of disputed claims.

In previous work, we have built Dispute Finder~\cite{Ennals2010}, a web browser extension that informs a user if the page they are browsing appears to make claims that are disputed by other sources. In the future, we intend that Dispute Finder will consult our corpus of disputed claims to determine whether claims made on a web page are disputed.

In future work, we intend to apply a similar dispute-finding approach to many other sources of information. We are working on a tool that listens to conversations and informs a user if they hear or say anything that is disputed by a reliable source. We are also interested in enhancing standard tools such as search engines, news aggregators, news readers, and email clients to inform a user if the information they are consuming may be disputed.

Since information may only become disputed after you read it, we are also interested in building tools that track all the information a user consumes and alert the user if something they read in the past ceases to be true, is corrected, or becomes disputed. Such a tool could also track the topics a user is interested in and inform the user when something new is disputed about the topic.

A third category of applications could be broadly classified as research tools: tools that allow a user to explore what is disputed about a particular topic, or to more broadly examine the social dynamics of disputes on the web. As an increasing proportion of human knowledge is brought to the web, these tools will be increasingly useful for sociological and historical research.

@@

We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 31st 2010, and for all dates from January 1st to January 31st for every year from 2000 to 2010. This gave us a total of 7 million text strings, of which 4.2 million were identified by our classifier as being unambiguous disputable claims. This does not mean that there are 4.2 million distinct beliefs that are disputed, since many of the claims in our corpus are repeating claims made elsewhere in the corpus.

@@

Figure~\ref{multiplot_nouns} shows the frequency with which the ten most common nouns were mentioned in particular years. For example the claim ``Obama is a muslim'' contains the nouns ``Obama'' and ``Muslim''. We used the NLTK~\cite{Bird2009} part-of-speech tagger to identify the nouns found in each of our claims. We then analyzed the distribution of noun frequencies in claims made between January 1st and January 31st of each year from 2000 to 2010. Although the dates we searched for were in January, the claims we found are often from other points in the year, due to the noisy nature of our date search mechanism (Figure~\ref{dateaccuracy}). We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns (Figure~\ref{multiplot_nouns}). All graphs are plotted on the same scale. The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made. It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even nouns prove to be quite interesting.

\begin{figure}[tbh]
 \begin{center}
  \begin{tabular}{|lll|}
    \hline
    {\bf Noun} & {\bf Word Cluster} & {\bf Freq} \\
    \hline
   {\bf god} & {\it no significant clusters} & \\
   \hline
   {\bf government} & health care & 2605 \\
                    & united states & 1710 \\
   \hline
   {\bf iraq} & weapons mass destruction & 3874 \\
              & united states & 2972 \\
	      & posed imminent threat & 2547 \\
	      & saddam hussean & 2088 \\
	      & damaging manner justify armed forces & 1814 \\
	      & national security interests & 1673 \\
	      & use nation & 1503 \\
	      & al qaeda & 1200 \\
   \hline
   {\bf israel} & united states & 1211 \\
		& middle east & 556 \\
		& off map & 543 \\
                & west bank & 426 \\
		& second coming & 296 \\
   \hline
   {\bf jesus}  & {\it no significant clusters} & \\
   \hline
   {\bf money}  & root evil & 503 \\
   \hline
    {\bf obama} & working best interests & 1077\\
                & health care & 1074\\
	        & united states & 741 \\
		& birth certificate & 434 \\
		& nobel prize & 311 \\
   \hline
   {\bf president} & united states & 1695 \\
		   & white house & 716 \\
		   & george w & 618 \\
		   & health care & 491 \\
		   & saddam hussein & 369 \\
		   & off map & 363 \\
		   & mahmoud ahmadinejad & 320 \\
		   & sarah palin & 277 \\
   \hline
      {\bf war} & united states & 1323 \\
		& mass destruction & 484 \\
		& middle east & 421 \\
   \hline

   {\bf women} & {\it no significant clusters} & \\
   \hline
  \end{tabular}
 \end{center}
 \caption{Largest word clusters found for nouns}
  \label{cluster-figure}

@@

We manually inspected our claims to determine what was going on in the world that made particular nouns spike at particular times:

\begin{itemize}
 \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention. His level of controversy then rose in 2008, in the run up to the November 2008 US presidential elections and then again after he became president. We believe that most of the mentions of Obama before 2004 are due to date classification errors.
 \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006}.
 \item {\bf Iraq:} The biggest spike seems to correspond to the initial invasion in 2003.
 \item {\bf Israel:} Spikes seem to correspond to the 2009 Gaza conflict and the 2006 Lebanon conflict.
\end{itemize}

These graphs are similar to those produced by MemeTracker~\cite{Backstrom2009}, which graphed the times when particular memes were discussed on the web. MemeTracker tracked frequently occurring phrases, rather than nouns used in disputed claims. Kittur et al~\cite{Kittur2009} graphed the categories on Wikipedia that contained the most conflict.

@@

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. For each cluster, the count is the number of claims about that noun that contain all of the words in the cluster. Most of these will make sense to people who have been following news in the United States. For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see discussion about President Ahmadinejad's alleged statement that Israel should be wiped off the map (which the authors had not previously realized was disputed). Some of the word clusters are not particularly interesting; for example many claims talk about the United States, even when that is not an important part of what is disputed.

It would be interesting to see how these word clusters compare to word clusters for all sentences on the web about these nouns, including those that are not disputed. Unfortunately we do not currently have access to such data.
